---
title: "Transsiz data"
output: 
  pdf_document:
  latex_engine: xelatex
  sansfont: Open Sans
  md_document: default
header-includes:
- \usepackage{graphicx}
- \usepackage{float}
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(extrafont)
library(tidyverse)

## Set default ggplot2 font size and font familly

loadfonts(quiet = TRUE)
theme_set(theme_bw(base_size = 12, base_family = "IBM Plex Sans"))
```

# Transsiz

Repository for the [Transsiz expedition](http://polarforskningsportalen.se/en/arctic/expeditions/transsiz).

## Pyranometer

This graphic show hourly averaged pyranometer data.

```{r}
pyrano <- read_csv("data/clean/pyranometer.csv")

pyrano %>%
  ggplot(aes(x = hour, y = par_just_below_surface_µmol)) +
  geom_line() +
  geom_point() +
  facet_wrap(~ station) +
  scale_y_continuous(breaks = seq(200, 1500, by = 200))
```

## ROV data

- Transmittance files used: `rovT_irrad`.
- Observations with `pitch` and `roll` between -10 and 10 degrees were kept.
- Ice thickness was estimated as: *ice_thickness = depth_water_m - dist_sea_ice_bottom_m*
- Using each ROV transmittance measurments, PAR0- (measured by the pyranometer) was propagated in the water column. 

## SUIT data

- Transmittance files used: `Ir_Dist_draft01_b.dat`.
- Depth of measurement (draft) was assumed to reflect the transmittance just below ice (i.e. transmittance_ed0).
- Only haul number was specified in transmittance files. Station id was matched with the file `Summary_file_PS92.txt`.
- Lat/long were extracted in files like `Lat_lon_01.dat` where the last part of the file name reflects the haul number.

## Matching SUIT and ROV transmittance data

There was some ROV stations without matching SUIT measurements. After discussions, we came up with this table that will link stations.

| ROV 	| SUIT    	|                                           	|
|-----	|---------	|-------------------------------------------	|
| 19  	| 19      	|                                           	|
| 27  	| 27      	|                                           	|
| 31  	| **28**  	| No match, so use a different SUIT station 	|
| 32  	|         	| We forget this station                    	|
| 39  	| 39      	|                                           	|
| 43  	| 43      	|                                           	|
| 46  	| ** 45** 	| No match, so use a different SUIT station 	|
| 47  	| 47      	|                                           	|

**For this study, we will use a total of seven stations 19, 27, 31, 39, 43, 46, 47.**

## Kd

Kd were calculated using vertical profiles made by the ROV at each station. Calculated Kd will be used to propagate pyranomater light using both ROV and SUIT transmittance data.

\begin{figure}[H]
\includegraphics{graphs/rov_vs_depth.pdf}
\end{figure}

\begin{figure}[H]
\includegraphics{graphs/rov_kd.pdf}
\end{figure}

## Propagating light in the water column

Light was propagated in the water column using the folowing equation:

\begin{equation}
\text{edz} = \text{par\_just\_below\_surface\_umol} \times e^{(-\text{kd} * \text{depth})} \times \text{transmittance\_percent\_ed0}
\end{equation}

Where $\text{par\_just\_below\_surface\_umol}$ is the irradiance measured by the pyranomater at 0-.